Misspecification Demonstration

### 2022-07-28 misspecification_study/misspec_demo.Rmd
add osa - problem encountered

@@

```{r runmodels}
if(file.exists(file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))){
  em_fits <- readRDS(file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))
} else {
  # run the models
  em_fits = list()
  for(m in 1:8){
    em_fits[[m]] = lapply(1:nsim, function(x){
      out = fit_wham(sim_input[[m]][[x]], 
                     do.osa = FALSE,
                     MakeADFun.silent = TRUE, 
                     retro.silent = TRUE, 
                     save.sdrep = FALSE)
      return(out)
    })
  }
  saveRDS(em_fits, file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))
}
```

@@

@@

@@

```{r plotemfit8}
# note could not get the following code to run within Rmarkdown (it produced the png files but not the pdf)
# can either pull this code out and run in console, or else uncomment and knit then comment and knit again
#em8.dir <- file.path(here(), "misspecification_study", "UR_em4")
#if(!dir.exists(em8.dir)){
#  dir.create(em8.dir)
#}
#plot_wham_output(mod=em_fits[[8]][[1]], dir.main=em8.dir)

@@

![catch 4 panel](UR_em4/plots_png/diagnostics/Catch_4panel_fleet_1.png)

![index 1 4 panel](UR_em4/plots_png/diagnostics/Index_4panel_1.png)

![index 2 4 panel](UR_em4/plots_png/diagnostics/Index_4panel_2.png)

![NAA age 1 4 panel](UR_em4/plots_png/diagnostics/NAA_4panel_1.png)

![NAA age 8 4 panel](UR_em4/plots_png/diagnostics/NAA_4panel_8.png)

![NAA residuals stacked barplot](UR_em4/plots_png/diagnostics/NAA_res_barplot_stacked.png)

@@

```{r lizretro}
# again had to run this in console because could not get it to knit
#em8lr.dir <- file.path(here(), "misspecification_study", "UR_em4", "liz_retro_plots")
#plot.retro.pars(m=em_fits[[8]][[1]], yr.plot.start=2005, od=em8lr.dir, save.name="UR_em4", 
#  plot.f='png' )
```

@@

![fleet selectivity](UR_em4/liz_retro_plots/UR_em4._fleet.sel.full.plot.png)

![index selectivity](UR_em4/liz_retro_plots/UR_em4._ind.sel.full.plot.png)

![NAA log deviations](UR_em4/liz_retro_plots/UR_em4._naa.devs.full.plot.png)

![Survey catchability](UR_em4/liz_retro_plots/UR_em4._q.full.plot.png)

>>>>

## Run the models

@@

```{r runmodels, results='hide'}
if(file.exists(file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))){
  em_fits <- readRDS(file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))
} else {
  # run the models
  em_fits = list()
  for(m in 1:8){
    em_fits[[m]] = lapply(1:nsim, function(x){
      out = fit_wham(sim_input[[m]][[x]], 
                     do.osa = TRUE,
                     MakeADFun.silent = TRUE, 
                     retro.silent = TRUE, 
                     save.sdrep = TRUE)
      return(out)
    })
  }
  saveRDS(em_fits, file.path(here(), "misspecification_study", "misspec_demo_fits.RDS"))
}
```

@@

## Correct data results

@@

## Under-reported catch data results

@@

```{r plotemfit8}
# ran into errors plotting the one-step-ahead residuals for each model
# ran the loop one model at a time to get output
#
# em_fits 1 and 5 gave error message
# Error in mod$osa[c(dat$keep_Cpaa[i, yind, ] + 1), ] : 
#   incorrect number of dimensions
#
# the other six em_fits gave error message
# Infinite osa residuals for aggregate catch in fleet  1 , so using +/-10 for range of y axis 
# Error in if (h > 0) max(1, ceiling(diff(range(x))/h)) else 1L : 
#   missing value where TRUE/FALSE needed
# In addition: Warning messages:
# 1: In min(x) : no non-missing arguments to min; returning Inf
# 2: In max(x) : no non-missing arguments to max; returning -Inf

# can either pull this code out and run in console, or else uncomment and knit then comment and knit again
# out.dir <- file.path(here(), "misspecification_study", "output")
# if (!dir.exists(out.dir)){
#   dir.create(out.dir)
# }
# mydir <- c(paste0("CC_em", 1:4), paste0("UR_em", 1:4))
# for (i in 1:8){
#   em.dir <- file.path(here(), "misspecification_study", "output", mydir[i])
#   if(!dir.exists(em.dir)){
#     dir.create(em.dir)
#   }
#   plot_wham_output(mod=em_fits[[i]][[1]], dir.main=em.dir)
# }
```

@@

![UR_em4 catch 4 panel](output/UR_em4/plots_png/diagnostics/Catch_4panel_fleet_1.png)

![UR_em4 index 1 4 panel](output/UR_em4/plots_png/diagnostics/Index_4panel_1.png)

![UR_em4 index 2 4 panel](output/UR_em4/plots_png/diagnostics/Index_4panel_2.png)

![UR_em4 NAA age 1 4 panel](output/UR_em4/plots_png/diagnostics/NAA_4panel_1.png)

![UR_em4 NAA age 8 4 panel](output/UR_em4/plots_png/diagnostics/NAA_4panel_8.png)

![UR_em4 NAA residuals stacked barplot](output/UR_em4/plots_png/diagnostics/NAA_res_barplot_stacked.png)

@@

```{r lizretro, eval = FALSE}
# again had to run this in console because could not get it to knit
# for (i in 1:8){
#   emlr.dir <- file.path(here(), "misspecification_study", "output", mydir[i], "liz_retro_plots")
#   if(!dir.exists(emlr.dir)){
#     dir.create(emlr.dir)
#   }
#   plot.retro.pars(m=em_fits[[i]][[1]], yr.plot.start=2005, od=emlr.dir, save.name=mydir[i], 
#                   plot.f='png' )
# }
```

@@

![UR_em4 fleet selectivity](output/UR_em4/liz_retro_plots/UR_em4._fleet.sel.full.plot.png)

![UR_em4 index selectivity](output/UR_em4/liz_retro_plots/UR_em4._ind.sel.full.plot.png)

![UR_em4 NAA log deviations](output/UR_em4/liz_retro_plots/UR_em4._naa.devs.full.plot.png)

![UR_em4 Survey catchability](output/UR_em4/liz_retro_plots/UR_em4._q.full.plot.png)

Interestingly, for estimation model 3, both the fits and the NAA log deviations showed a strong pattern of positive then negative or else negative then positive residuals over time.

![UR_em3 catch 4 panel](output/UR_em3/plots_png/diagnostics/Catch_4panel_fleet_1.png)

![UR_em3 index 1 4 panel](output/UR_em3/plots_png/diagnostics/Index_4panel_1.png)

![UR_em3 index 2 4 panel](output/UR_em3/plots_png/diagnostics/Index_4panel_2.png)

![UR_em3 NAA age 8 4 panel](output/UR_em3/plots_png/diagnostics/NAA_4panel_8.png)

![UR_em3 NAA residuals stacked barplot](output/UR_em3/plots_png/diagnostics/NAA_res_barplot_stacked.png)
